---
title: "TNA Structure Options"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, fig.width = 10, fig.height = 8, warning = FALSE, message = FALSE)
devtools::load_all(".")
```

## The Data: 10 Nodes, 2 Clusters

```{r}
set.seed(123)

# 10 nodes: 6 in GREEN cluster, 4 in BLUE cluster
nodes <- c("A", "B", "C", "D", "E", "F",   # GREEN (6 nodes)
           "G", "H", "I", "J")              # BLUE (4 nodes)

clusters <- list(
  GREEN = c("A", "B", "C", "D", "E", "F"),
  BLUE  = c("G", "H", "I", "J")
)

# Create weight matrix
n <- 10
mat <- matrix(0, n, n, dimnames = list(nodes, nodes))

# Within GREEN (stronger: 0.5-1.0)
for (i in 1:6) {
  for (j in 1:6) {
    if (i != j) mat[i, j] <- runif(1, 0.5, 1.0)
  }
}

# Within BLUE (stronger: 0.5-1.0)
for (i in 7:10) {
  for (j in 7:10) {
    if (i != j) mat[i, j] <- runif(1, 0.5, 1.0)
  }
}

# Between clusters (weaker: 0.1-0.4)
for (i in 1:6) {
  for (j in 7:10) {
    mat[i, j] <- runif(1, 0.1, 0.4)
    mat[j, i] <- runif(1, 0.1, 0.4)
  }
}

# Cluster assignment for each node
node_cluster <- c(rep("GREEN", 6), rep("BLUE", 4))
names(node_cluster) <- nodes
```

```{r results='asis'}
cat("🟢 **GREEN cluster (6 nodes):** A, B, C, D, E, F\n\n")
cat("🔵 **BLUE cluster (4 nodes):** G, H, I, J\n\n")
```

---

## Option A: FULL TNA (All Actual Weights)

All nodes can transition to all other nodes. Clusters = visual grouping only.

```{r fig.height=8}
row_sums <- rowSums(mat)
full_tna <- mat / ifelse(row_sums == 0, 1, row_sums)

net <- cograph(full_tna)
net$nodes$group <- node_cluster[net$nodes$label]

# Manual layout: GREEN on left, BLUE on right
layout_mat <- matrix(c(
  # GREEN (A-F) on left side
  0.15, 0.8,   # A
  0.05, 0.6,   # B
  0.05, 0.4,   # C
  0.15, 0.2,   # D
  0.25, 0.3,   # E
  0.25, 0.7,   # F
  # BLUE (G-J) on right side
  0.75, 0.8,   # G
  0.85, 0.6,   # H
  0.85, 0.4,   # I
  0.75, 0.2    # J
), ncol = 2, byrow = TRUE)
rownames(layout_mat) <- nodes

splot(net,
      layout = layout_mat,
      title = "A) FULL TNA: All actual node-to-node weights",
      node_fill = ifelse(node_cluster[net$nodes$label] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 12,
      edge_width_range = c(0.3, 2),
      edge_alpha = 0.5,
      edge_labels = TRUE,
      edge_label_size = 0.5)

# Add cluster labels
text(0.15, 0.95, "GREEN", col = "#4CAF50", font = 2, cex = 1.5)
text(0.80, 0.95, "BLUE", col = "#2196F3", font = 2, cex = 1.5)
```

---

## Option B: WITHIN-ONLY TNA (No Cross-Cluster Edges)

Only within-cluster transitions. **Zero edges between GREEN and BLUE.**

```{r fig.height=8}
cs <- cluster_summary(mat, clusters)

net2 <- cograph(cs$within_tna)

splot(net2,
      layout = layout_mat,
      title = "B) WITHIN-ONLY: No cross-cluster edges",
      node_fill = ifelse(node_cluster[net2$nodes$label] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 12,
      edge_width_range = c(0.3, 2),
      edge_alpha = 0.6,
      edge_labels = TRUE,
      edge_label_size = 0.55)

text(0.15, 0.95, "GREEN", col = "#4CAF50", font = 2, cex = 1.5)
text(0.80, 0.95, "BLUE", col = "#2196F3", font = 2, cex = 1.5)
```

---

## Option C: HYBRID UNIFORM

- Within-cluster: **actual weights**
- Between-cluster: **summary split equally** to all targets

```{r fig.height=8}
hybrid_uniform <- cs$within_tna

for (i in seq_along(clusters)) {
  for (j in seq_along(clusters)) {
    if (i != j) {
      src_nodes <- clusters[[i]]
      tgt_nodes <- clusters[[j]]
      uniform_val <- cs$tna[i, j] / length(tgt_nodes)
      for (src in src_nodes) {
        for (tgt in tgt_nodes) {
          hybrid_uniform[src, tgt] <- uniform_val
        }
      }
    }
  }
}
row_sums <- rowSums(hybrid_uniform)
hybrid_uniform <- hybrid_uniform / ifelse(row_sums == 0, 1, row_sums)

net3 <- cograph(hybrid_uniform)

splot(net3,
      layout = layout_mat,
      title = "C) HYBRID UNIFORM: Between = equal split",
      node_fill = ifelse(node_cluster[net3$nodes$label] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 12,
      edge_width_range = c(0.3, 2),
      edge_alpha = 0.5,
      edge_labels = TRUE,
      edge_label_size = 0.5)

text(0.15, 0.95, "GREEN", col = "#4CAF50", font = 2, cex = 1.5)
text(0.80, 0.95, "BLUE", col = "#2196F3", font = 2, cex = 1.5)
```

```{r}
cat("Cross-cluster weights from GREEN nodes to BLUE nodes:\n")
cat("(Notice: same value for each target)\n\n")
print(round(hybrid_uniform[1:3, 7:10], 3))
```

---

## Option D: HYBRID PROPORTIONAL

- Within-cluster: **actual weights**
- Between-cluster: **summary split by original ratios**

```{r fig.height=8}
hybrid_prop <- cs$within_tna

for (i in seq_along(clusters)) {
  for (j in seq_along(clusters)) {
    if (i != j) {
      src_nodes <- clusters[[i]]
      tgt_nodes <- clusters[[j]]
      original_block <- mat[src_nodes, tgt_nodes, drop = FALSE]
      block_row_sums <- rowSums(original_block)
      prop_block <- original_block / ifelse(block_row_sums == 0, 1, block_row_sums)
      for (s_idx in seq_along(src_nodes)) {
        for (t_idx in seq_along(tgt_nodes)) {
          hybrid_prop[src_nodes[s_idx], tgt_nodes[t_idx]] <- cs$tna[i, j] * prop_block[s_idx, t_idx]
        }
      }
    }
  }
}
row_sums <- rowSums(hybrid_prop)
hybrid_prop <- hybrid_prop / ifelse(row_sums == 0, 1, row_sums)

net4 <- cograph(hybrid_prop)

splot(net4,
      layout = layout_mat,
      title = "D) HYBRID PROPORTIONAL: Between = keeps ratios",
      node_fill = ifelse(node_cluster[net4$nodes$label] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 12,
      edge_width_range = c(0.3, 2),
      edge_alpha = 0.5,
      edge_labels = TRUE,
      edge_label_size = 0.5)

text(0.15, 0.95, "GREEN", col = "#4CAF50", font = 2, cex = 1.5)
text(0.80, 0.95, "BLUE", col = "#2196F3", font = 2, cex = 1.5)
```

```{r}
cat("Cross-cluster weights from GREEN nodes to BLUE nodes:\n")
cat("(Notice: different values per target, based on original)\n\n")
print(round(hybrid_prop[1:3, 7:10], 3))
```

---

## Side-by-Side Comparison

```{r fig.width=14, fig.height=12}
par(mfrow = c(2, 2), mar = c(1, 1, 3, 1))

# A) Full
net1 <- cograph(full_tna)
splot(net1, layout = layout_mat, title = "A) FULL TNA",
      node_fill = ifelse(node_cluster[nodes] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 10, edge_alpha = 0.4, edge_labels = TRUE, edge_label_size = 0.4)

# B) Within-only
net2 <- cograph(cs$within_tna)
splot(net2, layout = layout_mat, title = "B) WITHIN-ONLY",
      node_fill = ifelse(node_cluster[nodes] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 10, edge_alpha = 0.5, edge_labels = TRUE, edge_label_size = 0.45)

# C) Hybrid uniform
net3 <- cograph(hybrid_uniform)
splot(net3, layout = layout_mat, title = "C) HYBRID UNIFORM",
      node_fill = ifelse(node_cluster[nodes] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 10, edge_alpha = 0.4, edge_labels = TRUE, edge_label_size = 0.4)

# D) Hybrid proportional
net4 <- cograph(hybrid_prop)
splot(net4, layout = layout_mat, title = "D) HYBRID PROPORTIONAL",
      node_fill = ifelse(node_cluster[nodes] == "GREEN", "#4CAF50", "#2196F3"),
      node_size = 10, edge_alpha = 0.4, edge_labels = TRUE, edge_label_size = 0.4)
```

---

## Cluster-Level Summary (2x2)

```{r fig.width=6, fig.height=5}
between_net <- cograph(cs$tna)
splot(between_net,
      title = "BETWEEN-CLUSTER TNA (clusters as giant nodes)",
      node_fill = c("#4CAF50", "#2196F3"),
      node_size = 45,
      edge_labels = TRUE,
      edge_label_size = 1.0,
      edge_width_range = c(2, 4))
```

```{r}
cat("Cluster-to-cluster transition probabilities:\n")
print(round(cs$tna, 3))
```

---

## Summary

| Option | Within GREEN | Within BLUE | GREEN ↔ BLUE | Description |
|--------|-------------|-------------|--------------|-------------|
| **A) Full** | Actual | Actual | Actual | All original weights |
| **B) Within-Only** | Actual | Actual | **ZERO** | No cross-cluster |
| **C) Hybrid Uniform** | Actual | Actual | Summary/equal | Same weight to all targets |
| **D) Hybrid Proportional** | Actual | Actual | Summary/ratio | Keeps original proportions |
