---
title: "Community Visualization with cograph"
description: |
    Overlay community blobs on networks and visualize higher-order simplicial pathways
date: "2026-03-14"
author:
  - name: Mohammed Saqr
    url: https://saqr.me
    affiliation: University of Eastern Finland
  - name: Sonsoles López-Pernas
    url: https://sonsoles.me
    affiliation: University of Eastern Finland
citation:
  type: article
  author:
    - family: "Saqr"
      given: "Mohammed"
    - family: "López-Pernas"
      given: "Sonsoles"
categories:
  - tutorial
  - R
  - visualization
warning: false
message: false
fig.align: center
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: false
    code-tools: false
    theme: cosmo
    self-contained: true
execute:
  warning: false
  message: false
knitr:
  opts_chunk:
    fig.width: 8
    fig.height: 8
    dpi: 150
    comment: ""
---

```{r}
#| label: setup
#| include: false
library(tna)
devtools::load_all(".")
```

# Introduction

cograph provides two functions for visualizing community structure and higher-order relationships in networks:

- **`overlay_communities()`** --- renders a network with `splot()` and overlays smooth blob shapes highlighting communities
- **`plot_simplicial()`** --- visualizes higher-order pathways (simplicial complexes) as blobs on a ggplot2 canvas

Both accept any network type: `tna`, matrix, `igraph`, or `cograph_network`.

We use a TNA model of collaborative group regulation throughout:

```{r}
model <- tna(group_regulation)
```

# overlay_communities()

## Method Name

The simplest way: pass an igraph community detection method name. Partial matching and flexible naming are supported.

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, "walktrap")
```

Any igraph `cluster_*` method works: `"walktrap"`, `"louvain"`, `"fast_greedy"`, `"leading_eigen"`, `"infomap"`, `"leiden"`, `"label_prop"`, `"edge_betweenness"`, `"spinglass"`, `"optimal"`, `"fluid_communities"`. You can use the full igraph name (`"cluster_walktrap"`), the short name (`"walktrap"`), or a partial match (`"leading_eige"`). Directed graphs are automatically converted to undirected for detection.

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, "louvain")
```

## Named List

Define communities manually with a named list:

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, list(
  Regulatory = c("plan", "monitor", "adapt"),
  Social     = c("cohesion", "emotion", "consensus"),
  Task       = c("discuss", "synthesis", "coregulate")
))
```

## Membership Vector

A numeric vector or factor where each position maps to a node:

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, c(1, 1, 1, 2, 2, 2, 3, 3, 3))
```

## Communities Object

Pass a `cograph_communities` or `tna_communities` object directly:

```{r}
#| fig.width: 10
#| fig.height: 10
comm <- communities(model, method = "walktrap")
overlay_communities(model, comm)
```

## Custom Colors

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, list(
  Regulatory = c("plan", "monitor", "adapt"),
  Social     = c("cohesion", "emotion", "consensus"),
  Task       = c("discuss", "synthesis", "coregulate")
), blob_colors = c("#E8B4B8", "#B4D7E8", "#C5E8B4"), blob_alpha = 0.35)
```

## Overlapping Communities

Communities can share nodes:

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, list(
  "Self-Regulation" = c("plan", "monitor", "adapt", "emotion"),
  Collaboration     = c("cohesion", "consensus", "discuss",
                         "coregulate", "synthesis")
), blob_colors = c("#4FC3F7", "#fbb550"), blob_alpha = 0.30)
```

## Pass splot Arguments

All `...` arguments go to `splot()`:

```{r}
#| fig.width: 10
#| fig.height: 10
overlay_communities(model, list(
  Regulatory = c("plan", "monitor", "adapt"),
  Social     = c("cohesion", "emotion", "consensus"),
  Task       = c("discuss", "synthesis", "coregulate")
), title = "Group Regulation + Communities", minimum = 0.05)
```

# plot_simplicial()

Visualize higher-order pathways as smooth blobs. Source nodes are blue, target nodes are red.

## Basic Pathways

```{r}
#| fig.width: 10
#| fig.height: 10
plot_simplicial(model, c(
  "plan monitor -> adapt",
  "cohesion emotion -> consensus",
  "discuss synthesis -> coregulate"
), title = "Three Simplicial Pathways")
```

## Flexible Separators

Separators are auto-detected and tokens are validated against state names (case-insensitive):

```{r}
#| fig.width: 10
#| fig.height: 10
plot_simplicial(model, c(
  "plan, monitor -> adapt",
  "cohesion - emotion - consensus",
  "discuss synthesis coregulate"
), title = "Mixed Separator Styles")
```

## Dismantled View

One panel per pathway:

```{r}
#| fig.width: 8
#| fig.height: 8
plots <- plot_simplicial(model, c(
  "plan monitor -> adapt",
  "cohesion emotion -> consensus",
  "discuss synthesis -> coregulate"
), dismantled = TRUE)
```

## Custom Styling

```{r}
#| fig.width: 10
#| fig.height: 10
plot_simplicial(model,
  c("plan monitor -> adapt",
    "adapt monitor -> plan",
    "plan adapt -> monitor"),
  blob_colors = c("#B0D4F1", "#8BBDE0", "#6AA6CF"),
  blob_alpha = 0.30,
  blob_linewidth = 1.0,
  blob_line_alpha = 0.9,
  title = "Regulatory Cycle"
)
```

## No Network Needed

States are inferred from pathway strings when no network is provided:

```{r}
#| fig.width: 10
#| fig.height: 10
plot_simplicial(
  pathways = c("A B -> C", "C D -> E", "A E -> B"),
  blob_alpha = 0.30,
  title = "States Inferred from Pathways"
)
```
