---
title: "cograph — TNA Plotting Examples"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 8, fig.height = 7, dpi = 150,
  message = FALSE, warning = FALSE
)
devtools::load_all("/Users/mohammedsaqr/Documents/Github/cograph")
library(tna)
library(Saqrlab)
```

# 1. Single TNA Model — group_regulation

Build a TNA model from the `group_regulation` dataset (2000 sequences, 9 states).

```{r tna-model}
data(group_regulation)
model <- tna(group_regulation)
model
```

## Basic Network Plot

```{r plot-basic, fig.width=9, fig.height=8}
splot(model,
      title = "Group Regulation TNA",
      minimum = 0.05)
```

# 2. Bootstrap Analysis

Run bootstrap resampling (1000 iterations) to assess edge significance and confidence intervals.

```{r bootstrap, cache=TRUE}
set.seed(42)
boot <- bootstrap(model, iter = 1000)
```

```{r boot-summary}
sig_edges <- boot$summary[boot$summary$sig, ]
cat(sprintf("Significant edges: %d / %d\n", nrow(sig_edges), nrow(boot$summary)))
head(sig_edges[order(sig_edges$p_value), ], 10)
```

## Bootstrap — Significant Edges Only

```{r plot-boot-sig, fig.width=9, fig.height=8}
splot(boot,
      display = "significant",
      title = "Bootstrap — Significant Edges",
      show_stars = TRUE)
```

## Bootstrap — Full Network with Styling

Non-significant edges shown as dashed gray lines.

```{r plot-boot-styled, fig.width=9, fig.height=8}
splot(boot,
      display = "styled",
      title = "Bootstrap — Styled (sig=solid, nonsig=dashed)",
      show_stars = TRUE,
      minimum = 0.02)
```

## Bootstrap — Confidence Intervals

```{r plot-boot-ci, fig.width=9, fig.height=8}
splot(boot,
      display = "ci",
      title = "Bootstrap — With Confidence Intervals",
      show_ci = TRUE,
      minimum = 0.05)
```

# 3. Simulated Group TNA + Permutation Test

Generate two group TNA networks with Saqrlab, then compare with permutation testing.

```{r group-tna}
set.seed(123)
group_models <- Saqrlab::generate_group_tna_networks(2)
group_models
```

## Plot Each Group

```{r plot-groups, fig.width=14, fig.height=7}
par(mfrow = c(1, 2))
splot(group_models[[1]],
      title = "Group 1",
      minimum = 0.05)
splot(group_models[[2]],
      title = "Group 2",
      minimum = 0.05)
par(mfrow = c(1, 1))
```

## Difference Network

```{r plot-compare, fig.width=9, fig.height=8}
cograph::plot_compare(
  group_models[[1]], group_models[[2]],
  title = "Group 1 vs Group 2 — Difference Network")
```

## Permutation Test

```{r permutation, cache=TRUE}
set.seed(42)
perm <- tna::permutation_test(group_models[[1]], group_models[[2]], iter = 1000)
```

```{r perm-summary}
cat(capture.output(str(perm, max.level = 1)), sep = "\n")
```

## Permutation Test — Network

```{r plot-perm, fig.width=9, fig.height=8}
cograph::plot_permutation(perm,
      title = "Permutation Test — Significant Differences",
      show_nonsig = TRUE)
```

# 4. Simulated Sequences — Custom Group Comparison

Use `simulate_sequences()` to create two groups with different dynamics.

```{r simulate-custom}
# Simulate one large dataset and split into two groups
all_seq <- Saqrlab::simulate_sequences(
  n_sequences = 1000, seq_length = 15,
  n_states = 6, use_learning_states = TRUE,
  categories = "cognitive", seed = 10)

seq1 <- all_seq[1:500, ]
seq2 <- all_seq[501:1000, ]

model1 <- tna(seq1)
model2 <- tna(seq2)

cat("Model 1 states:", model1$labels, "\n")
cat("Model 2 states:", model2$labels, "\n")
```

## Compare Simulated Groups

```{r compare-sim, fig.width=14, fig.height=7}
par(mfrow = c(1, 2))
splot(model1, title = "Simulated Group A",
      minimum = 0.05)
splot(model2, title = "Simulated Group B",
      minimum = 0.05)
par(mfrow = c(1, 1))
```

```{r diff-sim, fig.width=9, fig.height=8}
cograph::plot_compare(model1, model2,
      title = "Simulated A vs B — Difference")
```

## Permutation on Simulated Data

```{r perm-sim, cache=TRUE}
set.seed(42)
perm_sim <- tna::permutation_test(model1, model2, iter = 500)
```

```{r plot-perm-sim, fig.width=9, fig.height=8}
cograph::plot_permutation(perm_sim,
      title = "Simulated Groups — Permutation Test",
      show_nonsig = TRUE,
      show_stars = TRUE)
```

## Bootstrap on Model 1

```{r boot-sim, cache=TRUE}
set.seed(42)
boot_sim <- bootstrap(model1, iter = 500)
```

```{r plot-boot-sim, fig.width=9, fig.height=8}
splot(boot_sim,
      display = "styled",
      title = "Simulated Group A — Bootstrap",
      show_stars = TRUE,
      minimum = 0.03)
```

---

*Generated with cograph v`r packageVersion("cograph")` + tna v`r packageVersion("tna")` + Saqrlab*
